Untitled Draft

### 2023-01-24 doc/manuscript.Rmd
Add preliminary analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-targets, include=FALSE}

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "..")
setwd("..")
source("R/utils.R")
source("R/model_builder_RQ1.R")
```

```{r load-targets, include=FALSE}
library(targets)
library(gt)
require(ggplot2)
tar_load(model_list)

@@

```{r out.width="100%"}

model_list[[1]] |> 
  plot_effects_RQ1(terms = c("pa_volume", "age_cat")) +
  facet_grid(cols = vars(group))
```

## Model tables

```{r results = "asis"}

tables <- lapply(model_list, function(x) x$table)
sapply(seq_len(length(tables)), function(x){

  cat("## ", names(tables)[x])
  tables[[x]] |> 
    gt() |> 
    apa_style() |> 
    as_raw_html() |> 
    cat()

  cat("\\n")
  cat("\\n")
})
